### 2010-06-17 pkg/paper/Draft/draft-Z-W.tex
some preliminary information for GL use in literature, more to come
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/glogis@14 b679b2f7-6539-45d0-a605-5ddcb976cde9

@@

>>>>

% something more about the reason to use GL

% Book Johnson 95 on logistic distribution

- income distributions, otherwise often used as growth models, or rainfall models
- definition of the distribution Abberger uses here is a generalization of 23.7 in Johnson 95 (shape ist halt hier zustätzlich noch dabei)
- longer tails than normal distribution, nonsymmetric (which is a clear net gain)
- more peaked in the center (net gain)
- the things above apply to the logistic distribution, not implicitely the GL

% searchterm for these ``generalized logistic distribution''
% found via Google Scholars
- in 2005-kjm-olp-gl2 it is shown, that the distribution used here is; cdf is given by: $1-\frac{\exp{-bx}}{(1+\exp{-x})^b}$ (given in this paper)
- 2005-spl-won-parametersarmitgld: here the GL is used (they find for Autoregressions that mostly data simply is not normal or student, so they use the GL-distribution (which is only somewhat slightly differently specified)
- 2000-ael-har-stockreturns: with almost the same reasoning as above used to model stock exchange data (not exactly gl as here but can be simplified to GL)
- 1999-cis-won-asyminnogl: almost the same as the 2005 paper (won.. is also the author :)
- 2007-tejof-kon-vatriskgstock: same use
- 2001-joae-wa-garchgl: similar (not exactly using gl but very similar)

% Econ Papers
- often in financial return data (which has high peakes)
- in gene expression data (since gl hast longer tails)

% eu database
% ideas
% citeceer
% econometric society
% questia
% ecb
% jstor
% springerlink
% ebsco
% wiley
% sciencedirect
% informaworld

% Abberger Publikation: Abberger, K., Heiler, S. 	Simultaneous estimation of parameters for a generalized logistic distribution and application to time series models 	2000 	84 	041-049 	A Allgemeines Statistisches Archiv/Journal of the German Statistical Society

- in 1987-eco-bat-inflationexpectation: the expected inflation is modelled as coming from a logistic distribution

@@

Some History for easier interpretation:

% this one from history-emu.pdf

eleven countries had met the Maastricht Criteria by 1997, allowing the
European monetary union to be launched in 1999. Greece was further behind in
meeting the criteria and only joined the monetary union in 2001.
First, entry into the euro was a much bigger structural shock for "peripheral"
member countries such as Greece, Ireland, Portugal, and Spain than for "core"
member countries like Germany and France. In particular, while all euro member
countries have enjoyed lower real interest rates under monetary union, the relative
decline was much greater for the countries on the periphery.
Second, membership in a monetary union can amplify the asymmetric impact
of certain shocks. A common nominal interest rate implies that persistent differences
in national inflation rates translate into differences in real interest rates across member countries: countries with relatively higher medium-term inflation
enjoy lower real interest rates than those with below-average inflation-stimulating
demand, credit growth, and housing markets in the former group
The Netherlands has lived though a
boom-bust cycle since the euro started, with a credit boom and high inflation in
1999-2001 followed by a contraction in economic activity that has reversed some of
the country's real appreciation against partner countries.
Of course, the destabilizing features of European monetary union for the
member countries do not mean that currency union has led to a net increase in
macroeconomic instability. The European Central Bank has been successful in
anchoring medium-term inflation expectations across the euro area at an annual
rate around 2 percent. At least for some countries, the attainment of such stability
outside the euro framework may have been a more costly process.

\section{Results}

% in money-growth regime switchin:
Germany: early 90ies: low inflation/ mid-end 90ies: high / and afterwards low
UK: low regime

just as a help

 wenn ma was siat dass as co-movement git: \cite{vandi} "`euro area countries move from essentially idiosyncratic inflation to co-movement in the mid-1980s"' (p. 2); "`price shocks in one country not transmitted to another"'; "`correlations remain stable until 1999 but then jumps sharpely"'; (2009-mwp-dijk-internationalinfl)

wenn was passiert: zitieren von Carporale: in their estimate \cite{cap} find that each country has at least one of the parameters of their variance estimates significantly different from zero, which is a clear indication of change in volatility as well.

falls Volatilität erhöht wird, verweise auf die Debatte in: $2004-wp-minford-ukjoiningemu$, die von einer Erhöhung der britischen Inflationsrate sprechen, sollte UK der EMU beitreten.

falls kleine Länder auffälliges Verhalten zeigen: $2008-wp-arnold-inflationuncertainty$, "`This suggests that within EMU, inflation uncertainty may increase in countries that have a smaller influence on ECB policy."' Ihre Begründung: "`For economic agents in small regions which are hit by positive inflation shocks, it will be uncertain how and when the increase
in inflation will be reversed. This results from imperfect information on the macroeconomic adjustment mechanism combined with the absence of a central bank dedicated to stabilizing their regional inflation rate. This does not hold true for the larger regions in the union, who have a largerweight in aggregate inflation and may therefore count on the price stability objective of the union’s central bank."'
vergleichen mit den Ergebnissen auf S.343 (country size and inflation uncertainty).

berücksichtige die DM Zone (Deutschland, Österreich, Luxemburg, Belgien und Holland), eventuell ähnlich

Caporale (ausgedruckt im Diss-Aktuell Ordner) finds that in the post-Euro area there are still significant inflation differentials across countries.

Wenns grosse Unterschiede zwischen den EMU Ländern gibt: ba Caporale stoht: "`the ECb itself admits that monetary policy can only affect price developements in the Euro area as a whole and cannot influence inflation differentials across regions (The Monetary Policy of the ECB, 2004)."' Und dort findet sich auch: "`some short-term volatility is inevitable given the fact that monetary policy can only affect prices wiht long and uncertain lags, hence the focus of the ECB on medium-term price stabilisation."'

Um den Anstieg in der Volatilität zu verteidigen: Caporale finds that steady state uncertainty has increased in eight out of twelve countries (p.966) (ie. Germany, France, Italy, Spain, Ireland, Finland, Luxembourg and Austria).

Zum Abgleich für Break dates: Caporale Table 5.

Wenn Ergebnisse da sind: abgleichen bei Caporale mit seiner Fig. 2, Fig. 3

falls Österreich und Spanien komisch: Wilfing findet, dass Schilling und Peseta nicht zu ihrer fixen Parität konvergiert sind

falls man grosse Unterschiede in der Volatilität sehen würde: $2008-wp-campolmi-laborinflvol$ point out that this can be explained by country specific labor market institutions.

 morana paper: S.10 untersucht convergence, je nachdem, was sich findet herausfinden, was wie ähnlich ist

 bei grossen Unterschieden: Busetti S.6: 3 Clustergruppen: Ger, Fra, Bel, Aut, Fin; Spa, Gre, Por, Ireland; Ned und It
